An Embedding Framework for Consistent Polyhedral Surrogates

### 2022-05-24 poly-embed-journal/poly-embed-journal.tex
Pass on the conclusion

\section{Conclusions} \label{sec:conclusion}
In this paper, we introduce and demonstrate the applicability of the embedding framework to construct calibrated polyhedral surrogates for finite prediction tasks.
We show that a convex surrogate embedding a target loss via the introduced framework is equivalent to the surrogate and target loss having matching Bayes risks and that their ``trimmed'' forms are equal as well.
Moreover, given an embedding, we give a link construction and show that a surrogate embedding a target loss implies the surrogate and a link given by our construction together are \emph{calibrated} with respect to the target loss.
Moreover, we show examples from the literature which demonstrate the broad applicability of our framework. \jessiet{Sentence on surrogate regret bounds?}

\paragraph{Open directions}
\jessie{Dimensionality, geometry of losses, more applications}
Several open directions of remain.
First, \citet{finocchiaro2020embedding} introduce preliminary lower bounds on embedding dimension (e.g., the lowest $d \in \mathbb{Z}$ such that $L : \reals^d \to \reals_+^\Y$ embeds $\ell$) based on optimality conditions that they derive.
However, it is unclear if these bounds are tight or if they can be improved by leveraging information about adjacent level sets of an embedded property.
Moreover, the relationship between embedding dimension and other notions of prediction dimension (e.g., convex calibration dimension, convex elicitation complexity) remains to be understood in dimensions greater than $1$.

Since polyhedral surrogates have a finite trimmed loss, it is an open line of work to relate embeddings to the geometry of losses~\citep{williamson2014geometry} through superprediction sets, as these sets encapsulate losses that are dominated by elements of $\trim(L)$.

Finally, while we work through applications of the framework to different target losses, we can imagine more target losses for which the embedding framework might be useful, such as multilabel learning, ranking, and (multiclass) structured prediction problems.
Understanding the application of embeddings to these settings, as well as the empirical performance of algorithms optimizing embeddings remains to demonstrate the empirical use of the framework.

>>>>

\section{Conclusions} \label{sec:conclusion}
In this paper, we introduce the embeddings framework to obtain convex and consistent surrogates for discrete prediction tasks, showing consistency by providing a link function construction.  
We show that a convex surrogate embedding a target loss via the introduced framework is equivalent to the surrogate and target loss having matching Bayes risks and that their ``trimmed'' forms are equal as well.
Finally, we show examples from the literature which demonstrate the broad applicability of our framework, ranging from high-confidence classification to structured prediction and others. \jessiet{Sentence on surrogate regret bounds?}

\paragraph{Open directions}
\jessie{Dimensionality, geometry of losses, more applications}
Several open directions of remain.
First, while \citet{finocchiaro2020embedding} introduce preliminary lower bounds on embedding dimension (e.g., the lowest $d \in \mathbb{Z}$ such that $L : \reals^d \to \reals_+^\Y$ embeds $\ell$) based on optimality conditions that they derive, it is unclear if these bounds are tight or if they can be improved by leveraging information about adjacent level sets of an embedded property.
Moreover, the relationship between embedding dimension and other notions of prediction dimension (e.g., convex calibration dimension, convex elicitation complexity) remains to be understood in dimensions greater than $1$.

Since polyhedral surrogates have a finite trimmed loss, it is an open line of work to relate embeddings to the geometry of losses~\citep{williamson2014geometry} through superprediction sets, as these sets encapsulate loss vectors that are dominated by elements of $\trim(L)$.

Finally, while we work through applications of the framework to different target losses, we can imagine more target losses for which the embedding framework might be useful, such as multilabel learning, ranking, and (multiclass) structured prediction problems.
Understanding the application of embeddings to these settings, as well as the empirical performance of algorithms optimizing embeddings remains to demonstrate the empirical use of the framework. \jessiet{I don't like this sentence}
